---
title: "Quoll Foraging"
author: "Riley M. Anderson"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
graphics: yes
output:
  github_document:
    toc: yes
    toc_depth: 5
    pandoc_args: --webtex
  html_document:
    keep_md: yes
    theme: readable
    mathjax: default
  html_notebook:
    code_folding: hide
    theme: readable
    mathjax: default
  pdf_document:
    toc: yes
header-includes:
  \usepackage{float}
  \floatplacement{figure}{H}
editor_options:
  chunk_output_type: console
---

```{r setup, include = F}
# @@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@
# @@@@@ Knitr Options
# @@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@

# Set root directory to the project directory
knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())


# Set default knitr options: 
# Suppress warnings and messages, cache chunks, 
#  set default figure size to 6x8 at 300 dpi, and save a png and pdf
knitr::opts_chunk$set(warning = F, message = F, collapse = T, cache = T,
    fig.height = 6, fig.width = 8, dpi = 300, # 6x8" @ 300dpi:1800x2400=4.3MP
    dev = 'png', dev.args = list(pdf = list(onefile = F)))

```



## Overview

What is this analysis about?

### Summary of Results
* 

```{r Main_Code, include = F, cache = F}

# @@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@
# @@@@@ Setup - This code is run, but output is hidden
# @@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@

# Load Packages
library(tidyverse) # Needed for data wrangling: dplyr, tidyr, ggplot2
library(cowplot) # Needed for publication-quality ggplots
library(ggridges)
library(glmmTMB)
library(emmeans)
library(sjPlot)
library(knitr)

# @@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@
# @@@@@ Data Preparation
# @@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@

# Import datasets
detections <- read.csv("data/VertsBehaviorDataAll.csv")

species <-  read.csv("data/VertsBehaviorDataDiscoveryInitiateForaging.csv")

# Functions

# Function to check for overdispersion in poisson and binomial models:

overdispersion_test <- function(model, type = "pearson"){
    # Get the pearson residuals
    residuals <- resid(model, type = type)
    # Get the residual degrees of freedom of the model
    df <- df.residual(model)
    # Sum of residual deviance
    dev <- sum(residuals ^ 2)
    # Overdispersion = sum of squared residuals / residual degrees of freedom
    ratio <- round(dev / df, 3)
    # P-value 
    pvalue <- round(pchisq(dev, df, lower.tail = FALSE), 3)
    # Get the formula
    f = paste(as.character(formula(model))[2:3], collapse = " ~ ")
    # Get the model name
    name <- deparse(substitute(model))
    cat("Overdispersion ratio for model:", name, "\nformula:", f, 
        "\n\nAcceptable range: 1 - 1.4\nOverdispersion ratio:",
        ratio, " df:", df, " p =", pvalue, "\n", 
        ifelse(pvalue < 0.05, "Data are overdispersed\n", 
        "Data are not overdispersed\n"))
    # Return all the parameters
    return(c(ratio = ratio, deviance = dev, df = df, pvalue = pvalue))
}


```


```{r Data_Wrangling, echo = F, comment = ""}


detections <- detections %>% 
  mutate(start = parse_date_time(start, "%m/%d/%Y %H:%M"),
         end = parse_date_time(end, "%m/%d/%Y %H:%M"),
         established = parse_date_time(established, "%m/%d/%Y %H:%M"),
         first_consumption = parse_date_time(first_consumption,
                                             "%m/%d/%Y %H:%M"),
         discover = parse_date_time(discover, "%m/%d/%Y %H:%M"),
         across(c(species, site, replicate, treatment, devil_poa,
                  season, carcass_present, first_species), factor))

```

## Scavenger abundance
```{r scav_abund, echo = F}

detections %>% 
  group_by(species, season) %>% 
  tally() %>% kable(format = "markdown")

```


## Vigilance

### Vigilance by devil presence or absence, site, and season
```{r vigilance_devil_pres_abs_site_season, echo = F}

detections %>% 
  filter(species == "Spotted-tailed quoll" &
           devil_poa != "NA") %>% 
  ggplot(aes(x = total, y = vigilant,
             color = devil_poa)) +
  geom_point() +
  geom_smooth(method = 'lm', show.legend = F) +
  facet_wrap(vars(season, site), scales = "free") +
  theme(strip.background = element_blank()) +
  theme_minimal() +
  labs(x = "Total photos",
       y = "Vigilant photos",
       color = "Devils")


vig_mod1 <- glm(cbind(vigilant, total) ~ season * devil_poa +
                  carcass_present,
                family = quasibinomial(),
                data = filter(detections,
                              species == "Spotted-tailed quoll" &
                                devil_poa != "NA"))
overdispersion_test(vig_mod1)
summary(vig_mod1)
plot_model(vig_mod1, type = "pred",,
           terms = c("season", "devil_poa"))
plot_model(vig_mod1, type = "est") +
  geom_hline(yintercept = 1, linetype = 2)


```



### Vigilance by devil presence or absence.
```{r vigilance_devil_pres_abs, echo = F}

detections %>% 
  filter(species == "Spotted-tailed quoll" &
           devil_poa != "NA") %>% 
  ggplot(aes(x = total, y = vigilant,
             color = devil_poa)) +
  geom_point() +
  geom_smooth(method = 'lm', show.legend = F) +
  theme(strip.background = element_blank()) +
  theme_minimal() +
  labs(x = "Total photos",
       y = "Vigilant photos",
       color = "Devils")

vig_mod3 <- glm(cbind(vigilant, total) ~ devil_poa,
                family = quasibinomial(),
                data = filter(detections,
                              species == "Spotted-tailed quoll" &
                                devil_poa != "NA"))
summary(vig_mod3)
plot_model(vig_mod3, type = "pred")
```

### Vigilance by carcass treatment, site, and season (E = excluded, S = access).
```{r vigilance_devil_treatment_site_season, echo = F}

detections %>% 
  filter(species == "Spotted-tailed quoll") %>% 
  ggplot(aes(x = total, y = vigilant,
             color = treatment)) +
  geom_point() +
  geom_smooth(method = 'lm', show.legend = F) +
  facet_wrap(vars(season, site), scales = "free") +
  theme(strip.background = element_blank()) +
  theme_minimal() +
  labs(x = "Total photos",
       y = "Vigilant photos",
       color = "Carcass\ntreatment")

```


### Vigilance by carcass treatment (E = excluded, S = access).
```{r vigilance_devil_treatment, echo = F}

detections %>% 
  filter(species == "Spotted-tailed quoll") %>% 
  ggplot(aes(x = total, y = vigilant,
             color = treatment)) +
  geom_point() +
  geom_smooth(method = 'lm', show.legend = F) +
  theme(strip.background = element_blank()) +
  theme_minimal() +
  labs(x = "Total photos",
       y = "Vigilant photos",
       color = "Carcass\ntreatment")

```

## Foraging

### Foraging by devil presence or absence, site, and season
```{r foraging_devil_pres_abs_site_season, echo = F}

detections %>% 
  filter(species == "Spotted-tailed quoll" &
           devil_poa != "NA") %>% 
  ggplot(aes(x = total, y = foraging_carc,
             color = devil_poa)) +
  geom_point() +
  geom_smooth(method = 'lm', show.legend = F) +
  facet_wrap(vars(season, site), scales = "free") +
  theme(strip.background = element_blank()) +
  theme_minimal() +
  labs(x = "Total photos",
       y = "Foraging photos",
       color = "Devils")

```



### Foraging by devil presence or absence.
```{r foraging_devil_pres_abs, echo = F}

detections %>% 
  filter(species == "Spotted-tailed quoll" &
           devil_poa != "NA") %>% 
  ggplot(aes(x = total, y = foraging_carc,
             color = devil_poa)) +
  geom_point() +
  geom_smooth(method = 'lm', show.legend = F) +
  theme(strip.background = element_blank()) +
  theme_minimal() +
  labs(x = "Total photos",
       y = "Foraging photos",
       color = "Devils")

```

### Foraging by carcass treatment, site, and season (E = excluded, S = access).
```{r foraging_devil_treatment_site_season, echo = F}

detections %>% 
  filter(species == "Spotted-tailed quoll") %>% 
  ggplot(aes(x = total, y = foraging_carc,
             color = treatment)) +
  geom_point() +
  geom_smooth(method = 'lm', show.legend = F) +
  facet_wrap(vars(season, site), scales = "free") +
  theme(strip.background = element_blank()) +
  theme_minimal() +
  labs(x = "Total photos",
       y = "Foraging photos",
       color = "Carcass\ntreatment")

```


### Foraging by carcass treatment (E = excluded, S = access).
```{r foraging_devil_treatment, echo = F}

detections %>% 
  filter(species == "Spotted-tailed quoll") %>% 
  ggplot(aes(x = total, y = foraging_carc,
             color = treatment)) +
  geom_point() +
  geom_smooth(method = 'lm', show.legend = F) +
  theme(strip.background = element_blank()) +
  theme_minimal() +
  labs(x = "Total photos",
       y = "Foraging photos",
       color = "Carcass\ntreatment")

```


## Session Information

```{r Session_Info, echo = F, comment = ""}

# Add session information to help with reproduceability
sessionInfo()


```


